---
title: "Variable Descriptions"
output: pdf_document
---


This file is simply met to keep track of all of the variables that are in the code.



input$
input$

Welcome Page
Creditenial
username: employee's username
password: employee's password

Renter
length_of_rental: either single or multiday rental

exclusive to length_of_rental = 'single'
	amount_of_people: select the amount size of the boat that you want
	dates_of_rental: select a single date
	len_day: full or half day
	boat_to_rent_single: automattically comes up with boat numbers that are available, user selects one





exclusive to length_of_rental = 'multi'
	dates_of_rental_multi: starting and ending dates
	size_to_rent_multi: you select the size that you would like to rent


check availability button: checks to see what boats are available for that day, gives multiday a table output

first_name_rental_boater: the first name of the renter
last_name_rental_boater: the last name of the renter
email_rental_boater: the email of the rental boater
phone_rental_boater: the phone number of the rental boater
address_rental_boater: the address of the rental boater
time_slot: time slot that the boater should have


tube_rental: yes or no if they want a tube
cost_of_tube: employee puts the price of the tub rental in


confirm_rental_button:
	confirms the rental for both multiday and single day. Will describe both processess in detail later.







Camper

Service

Calendar View

Cancelation

Edit Fleet
new_rental_number: the new rental boat number that is added to the fleet
max_people: the max amount of people for this rental boat
full_day_price_rental_addition: employee enters the price of this rental boat
half_day_price_rental_addition: employee enters the price of this rental boat


confirm_rental_addition:
	action button that adds the boat to the fleet

boat_to_remove: number of active boat to remove from the fleet
confirm_boat_removal:
	button that confirms the removal of this boat from the fleet

broken_boat_number: # of broken down boat
submit_broken_boat:
	action button that submits the broken boat

fixed_boat_number: # of boat that has been fixed
confirm_fixed_boat:
	confirm that the boat has been fixed



DO NOT RENT
do_not_rent_addition_email: email to put on the do not rent to list
do_not_rent_addition_description: reason they are put on that list
confirm_do_not_rent_addition: 
	button that puts them on the do not rent to list

do_not_rent_removal_email: email to remove from the do not rent to list
confirm_do_not_rent_removal: confirm the removal of that person from the do not rent to list



Email Send

Create New Email
Subscribed Customer Email

Customer Map

Customer Visualizations



size_to_rent_multi: max amount of people for multiday rental


active_boats: Boats that are currently able to be rented, and are not broken down

broken_boats: Boats that are currently able to be rented, but are broken down

rented_boats_for_multiday_length: contains the boats that are rented for the length of the multiday,
                                  the max amount of people, and filtered to be consistent with the amount
                                  of people that the user wants





the_boat_for_multiday_rb_number: All boats that have this number will be moved during the duration that the multiday
                                 boat is supposed to be rented will be moved. This is the number of the multiday that
                                 is coming into the database

the_boat_for_multiday_rb_id: same thing as above, just as the id number for that specific boat


moveable_rented_boats: Boats that are rented for the iterated day within the multiday's for loop. 
                       these boats have the same characteristics as the multiday. These boats need 
                       the following criteria: must not be a multiday at any time during the multiday-to-rent's time period,
                       must be the correct size





=================================================
manager page

new_employee_first_name
new_employee_middle_initial
new_employee_last_name
confirm_new_hire

name_staff_leaving
confirm_staff_leaving
=================================================










```{r}
m<-outer(1:20,1:20,function(x,y) sin(sqrt(x*y)/3))

   redblue<-colorRampPalette(c("red","orange","blue"),method="linear")
   filled.contour(m,color.palette=redblue)

   yb<-colorRampPalette(c("yellow2","goldenrod","darkred"))
   filled.contour(m,color.palette=yb)

   yb<-colorRampPalette(c("yellow2","goldenrod","darkred"),bias=0.5)
   filled.contour(m,color.palette=yb)

   ## Two ColorBrewer sequential palettes
   ylOrBn4<-c("#FFFFD4", "#FED98E", "#FE9929","#CC4C02")
   ylGnBl5<-c("#FFFFCC","#C7E9B4","#7FCDBB","#40B6C4","#2C7FB8" ,"#253494")

   ylOrBn<-colorRampPalette(ylOrBn4,method="linear")
   ylGnBl<-colorRampPalette(ylGnBl5)
   filled.contour(m,color.palette=ylOrBn)
   filled.contour(m,color.palette=ylGnBl)
```








```{r}

df

"email","rental_id","name"


df_1 <- df %>%
  filter(name == "Jeff") %>%
  select(email,rental_id)
  
df_1


```






